%%%%%%%%%%%%%%%%%%%%%%%
% Title: Resume       %
% Author: Jacob Carey %
% Date: 4-26-14       %
%%%%%%%%%%%%%%%%%%%%%%%

% define icons to be used from fontawesome

\def\faGithub{\symbol{"F09B}}
\def\faLinkedin{\symbol{"F0E1}}
\def\faEnvelope{\symbol{"F003}}
\def\faPhone{\symbol{"F095}}

\documentclass[]{friggeri-cv} % use friggeri resume template
\usepackage{fontspec} % required for fontawesome
\usepackage{fontawesome} % required for icons used in about section

\begin{document}

% create header of format
% first last
% title

\header{jacob}{carey}{} 

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{about}
5633 Columbia Rd
Apt 304
Columbia, MD 21044
~
\href{tel:14342039317}{\faPhone +1 (434) 203 9317}
\href{mailto:jcarey15@jhu.edu}{\faEnvelope  jcarey15@jhu.edu}
\href{https://github.com/jacobcvt12}{\faGithub jacobcvt12}
\href{https://www.linkedin.com/in/jacobcvt12}{\faLinkedin jacobcvt12}
\section{programming}
C, C++, Java
Python, Django,
SQL, R
\section{tools}
git, Vim, Bash
\LaTeX
\section{environments}
Debian/Ubuntu
OS X
\section{skills}
Modeling \& simulation
Machine learning
Regression analysis
Linear programming
Time series analysis
Data visualization
Web scraping
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2014--Now}
{Master {\normalfont of Science in}
\href{http://www.jhsph.edu/departments/epidemiology/}{Epidemiology}}
{\href{http://www.jhu.edu}{Johns Hopkins University}}
{Infectious Diseases Concentration}
%------------------------------------------------
\entry
{2008--2012}
{Bachelor {\normalfont of Science in}
\href{https://www.math.vt.edu/}{Mathematics}}
{\href{http://www.vt.edu}{Virginia Tech}}
{Graduated with Honor}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2015--Present}
{Johns Hopkins University Department of Biostatistics}
{Baltimore, Maryland}
{\emph{Research Assistant}
\begin{itemize}
\renewcommand\labelitemi{--}
\item Develop software to perform statistical analysis of genomic data
\item Lead study of oncology data
\end{itemize}
}
%------------------------------------------------
\entry
{2014--Present}
{Johns Hopkins University Department of Epidemiology}
{Baltimore, Maryland}
{\emph{Research Assistant}
\begin{itemize}
\renewcommand\labelitemi{--}
\item Analysis and writeup of epidemiological studies
\end{itemize}
}
%------------------------------------------------
\entry
{2014}
{\href{http://www.marriott.com/}{Marriott International}}
{Bethesda, Maryland}
{\emph{Manager, eCommerce Analysis}
\begin{itemize}
\renewcommand\labelitemi{--}
\item Assisted with new Marriott user-centric sort order algorithm
\item Developed time series model to determine effectiveness of hotel promotions. 
\item Calculated weekly values of search engine keywords in order to best allocate online marketing funds.
\item Performed web scraping of external websites to provide business insights.
\item Worked with datasets greater than one billion rows.
\item Automated reports using R \& ggplot2 and ETL using Python scripts.
\end{itemize}
}
%------------------------------------------------
\entry
{2012--2014}
{\href{http://www.deloitte.com/}{Deloitte}}
{Arlington, Virginia}
{\emph{Data Analyst}
\begin{itemize}
\renewcommand\labelitemi{--}
\item Managed a client-facing team of three consultants in the analysis of datasets greater than one million rows using SAS. 
Led regular meetings and presented results and data visualizations to key clients and internal stakeholders.
\item Developed web application to be used by federal agencies to optimize resource allocation. 
Used Python to perform server-side calculations.
\item Assisted federal agency in meeting requirements of government act using sample selection and estimation of disbursed grants and transactions.
\end{itemize}
}
%------------------------------------------------
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	SOFTWARE SECTION
%----------------------------------------------------------------------------------------

\section{software}
\begin{entrylist}
\entry
{}
{\href{https://github.com/scristia/CNPBayes}{CNPBayes}}
{https://github.com/scristia/CNPBayes}
{\emph{Role: Author}
\begin{itemize}
\renewcommand\labelitemi{--}
\item Bayesian mixture model for estimating copy number polymorphisms
\end{itemize}
}
\end{entrylist}

\end{document}
